Research Ideas

### 2023-05-24 research/ideas.tex
added some research ideas

    $$f(\xb) = \underbrace{\fxs(x_s) +  \fxc(\xc)}_{f_{ni}(\xb)} + \kappa(\xc, x_s)$$

>>>>

    \[
      f(\xb) = \underbrace{\fxs(x_s) +  \fxc(\xc)}_{f_{ni}(\xb)} + \kappa(\xc, x_s)
    \]

    A simple approach is defining \(f\) to be a Neural Network and \(f_{ni}\) a Neural Additive Model without interaction
    between \(x_s\) and \(\xc\). Then \(\kappa(\xc, x_s) = f(\xb) - f_{ni}(\xb)\) and we quantify the importance of \(\kappa\) as \(\mathbb{E}_{X_c, X_s} \left [ |\kappa(X_c, X_s)| \right ] \approx \sqrt{\frac{1}{N} \sum_i \kappa^2(\xc, x_s)} \).
